Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}

### 2023-11-29 draft/draft.tex
presentation

\title{Air pollution and agricultural productivity in a developing country\footnote{I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference attendees at the 2023 KER International Conference and the University of Reading. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-07-19}

\begin{document}
\maketitle
\begin{abstract}
\noindent I document negative externalities of air pollution in the Indian agricultural sector. Using variation in pollution induced by changes in wind across years, I show that higher levels of pollution lead to decreased agricultural productivity. The negative effects of pollution are larger in areas growing more labor-intensive crops, indicating that the pollution works partly through direct effects on labor productivity. I also show that pollution from coal plants has a larger effect on agricultural productivity than other types of pollution. These results suggest that the negative externalities of pollution may hit the poorest particularly hard, given their reliance on agriculture.\\
\strut \\
\textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India\\
\textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53
\end{abstract}

@@

\caption{\label{tab:plantresultstable}Local characteristics and the construction of coal plants}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{1991 census} & \multicolumn{2}{c}{2001 census} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & 1991 & 2001 & 2001 & 2011\\
\midrule
Population (log) & 0.012*** & 0.009*** & 0.015*** & 0.006***\\
 & (0.001) & (0.000) & (0.000) & \vphantom{1} (0.000)\\
Area (log) & -0.010*** & -0.005*** & -0.010*** & -0.005***\\
 & (0.001) & (0.000) & (0.000) & (0.000)\\
Urban pop (prop) & -0.029 & 0.006 & -0.003 & -0.007\\
 & (0.037) & (0.035) & (0.022) & (0.018)\\
Ag. productivity &  &  & 0.014*** & 0.028***\\
 &  &  & (0.001) & (0.001)\\
Pollution (log PM 2.5) &  &  & 0.051*** & 0.016***\\
 &  &  & (0.002) & (0.001)\\
Sub-sample & all & no plant & all & no plant\\
\midrule
Observations & 283,021 & 264,265 & 508,786 & 469,005\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: State fixed effects are included in regressions. Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}c}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind days & -0.0078*** & -0.0065*** & -0.0051*** & -0.0053***\\
 & (0.0007) & (0.0007) & (0.0007) & (0.0007)\\
weather & No & Yes & Yes & No\\
weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

To put the size of the coefficient in context, it is worth digging a little deeper into the exposure variable. The mean within-village absolute deviation in wind exposure is approximately 2.42 days, meaning that the average change in agricultural productivity from year-to-year due to nothing but changes in wind patterns carrying particulate matter is around 1.5 percent relative to the mean. This implies that swings in agricultural productivity -- due to wind direction -- of several percent are probably quite common, since the absolute deviation includes deviations above and below the mean.

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}c}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Particulate matter (log PM 2.5) & -0.042*** & -0.045*** & -0.008** & -0.041***\\
 & (0.003) & (0.003) & (0.003) & (0.003)\\
Weather & No & Yes & Yes & No\\
Weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes\\
\midrule
Observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

Of course, it is not wind, per se, that we are interested in. Instead, we are actually interested in better understanding the effects of exposure to pollution on agricultural productivity. Table \ref{tab:yieldtablepm} presents the same regressions as Table \ref{tab:yieldtable}, with a key difference: instead of wind exposure, it uses log average concentration of \(\mathrm{PM 2.5}\) -- from Hammer et al. (2020) -- during the season as the key explanatory variable. There is again a consistent, negative relationship between particulate matter and agricultural productivity. Since both variables are logged, the coefficients are similar to elasticities, indicating that a one-percent increase in pollution leads to an approximately 0.04 percent decrease in agricultural productivity in three of the columns.

@@

I present these IV results in Table \ref{tab:yieldtabletwo}, with the first-stage F-statistic at the bottom. The first-stage results -- the full results are in Table \ref{tab:yield3ivmainfirststage} of the appendix -- make clear how strong of an instrument wind is; all three F-statistics are above 1,000, meeting even the higher bar for the first-stage F-test argued for by D. Lee et al. (2022).

@@

Figure \ref{fig:crops} shows the distribution of the most common crop across the villages in my sample. Though there are large areas where rice is the most commonly grown crop, there is also quite a bit of overlap, especially in the middle parts of the country. However, given the geographic concentration of rice production, I will implement a robustness check with state-by-year fixed effects below.

@@

@@

Importantly, since these results come from an IV, both coefficients denote the change in agricultural yield due to an increase in pollution by the same units. In other words, this is not identifying differences in overall pollution, per se, but rather differences in the effects of an increase of pollution by the same percentage. These different effects could be due to, for example, differences in emission patterns for different kinds of plants and factories; coal plants, for example, are responsible for much more mercury than other kinds of polluting industries.\footnote{\url{https://www.epa.gov/sites/default/files/2016-12/documents/nei2014v1_tsd.pdf}}

@@

@@

\caption{\label{tab:yield8cumulative}Cumulative exposure to pollution during the season}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2.25cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
June & -0.643*** &  &  &  & \\
 & (0.064) &  &  &  & \\
July &  & -0.658*** &  &  & \\
 &  & (0.045) &  &  & \\
Aug. &  &  & -0.531*** &  & \\
 &  &  & (0.049) &  & \\
Sept. &  &  &  & -0.672*** & \\
 &  &  &  & (0.047) & \\
Oct. &  &  &  &  & -0.943***\\
 &  &  &  &  & (0.069)\\
weather & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\midrule
F & 1,327 & 2,830 & 2,933 & 2,413 & 1,515\\
observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

>>>>

\title{Air pollution and agricultural productivity in a developing country\footnote{I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference attendees at the 2023 KER International Conference and the University of Reading. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-11-23}

\begin{document}
\maketitle
\begin{abstract}
\noindent I document negative externalities of air pollution in the Indian agricultural sector. Using variation in pollution induced by changes in wind across years, I show that higher levels of pollution lead to decreased agricultural productivity. The negative effects of pollution are larger in areas growing more labor-intensive crops, indicating that the pollution works partly through direct effects on labor productivity. I also show that pollution from coal plants has a larger effect on agricultural productivity than other types of pollution. A back-of-the-envelope calculation indicates that aggregate output losses from pollution are substantial; 2011 total output would have been between 2.3 and 4.5 percent higher if pollution had remained at 2001 levels, depending on the crop.\\
\strut \\
\textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India\\
\textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53
\end{abstract}

@@

\caption{\label{tab:plantresultstable}Local characteristics and the construction of coal plants}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{1991 census} & \multicolumn{2}{c}{2001 census} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & 1991 & 2001 & 2001 & 2011\\
\midrule
Population (log) & -0.107 & 0.291*** & 0.241*** & 0.128\\
 & (0.097) & (0.083) & (0.079) & (0.080)\\
Area (log) & 0.240*** & -0.110 & 0.133* & 0.119\\
 & (0.065) & (0.088) & (0.079) & (0.085)\\
Ag. productivity &  &  & 0.092 & 0.121\\
 &  &  & (0.070) & (0.097)\\
Pollution (log PM 2.5) &  &  & 0.612*** & 0.530**\\
 &  &  & (0.201) & (0.256)\\
Has plant? &  & 14.842*** &  & 13.574***\\
 &  & (0.568) &  & (0.158)\\
Observations & 209,110 & 209,110 & 408,913 & 415,334\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: State fixed effects are included in regressions. Robust standard errors are in parentheses. The outcome in the first column is whether the village is within 30km of a coal plant in 1991. The second column is whether a village in 1991 will have a coal plant in 2001, conditional on not having one in 1991. The last two columns are similarly defined, except using 2001 and 2011 as the years. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind days (10s) & -0.0078*** & -0.0065*** & -0.0051*** & -0.0053***\\
 & (0.0007) & (0.0007) & (0.0007) & (0.0007)\\
weather & No & Yes & Yes & No\\
weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

To put the size of the coefficient in context, it is worth digging a little deeper into the exposure variable. Wind is scaled by 10 for presentation, meaning that an increase in \emph{exposure} for a village from its mean leads to a 0.5 percent drop in agricultural productivity. The standard deviation of the within-village change in exposure to wind from polluted areas is 4.35, meaning a one-standard-deviation increase from the mean leads to a 0.22 percent decrease in agricultural productivity due to nothing but being located downwind from a pollution source.

Of course, it is not wind, per se, that we are interested in. Instead, we are actually interested in better understanding the effects of exposure to pollution on agricultural productivity. Table \ref{tab:yieldtablepm} in the appendix presents the same regressions as Table \ref{tab:yieldtable}, with a key difference: instead of wind exposure, it uses log average concentration of \(\mathrm{PM 2.5}\) -- from Hammer et al. (2020) -- during the season as the key explanatory variable. There is again a consistent, negative relationship between particulate matter and agricultural productivity. Since both variables are logged, the coefficients are similar to elasticities, indicating that a one-percent increase in pollution leads to an approximately 0.04 percent decrease in agricultural productivity in three of the columns.

@@

I present these IV results in Table \ref{tab:yieldtabletwo}, with the first-stage F-statistic at the bottom. The first-stage results -- the full results are in Table \ref{tab:yield3ivmainfirststage} of the appendix -- make clear how strong of an instrument wind is; all three F-statistics are above 1,000, meeting even the higher bar for the first-stage F-test argued for by D. Lee et al. (2022). The coefficient on wind in the first stage is stable at around 0.0085 across specifications.

@@

Figure \ref{fig:crops} in the appendix shows the distribution of the most common crop across the villages in my sample. Though there are large areas where rice is the most commonly grown crop, there is also quite a bit of overlap, especially in the middle parts of the country. However, given the geographic concentration of rice production, I will implement a robustness check with state-by-year fixed effects below.

@@

\begin{figure}
\includegraphics{draft_files/figure-latex/yield8monthly-1} \caption[Effects of pollution on productivity by month]{Effects of pollution on productivity by month}\label{fig:yield8monthly}
\end{figure}

Another way to tease out differential effects on labor productivity, specifically, is to look at the effects of pollution by month. If pollution is working through labor, then we would expect to see larger effects when labor is relatively more important than. The harvest season, the fifth month of the agricultural season in the data, stands out as the most likely candidate for two reasons. First, labor allocation is generally quite on plots during the harvest season. Second, pollution at the very end of the season is unlikely to have large effects on overall land producitivty, as opposed to pollution in prior months.

Figure \ref{yield8monthly} presents the coefficients of the IV regression separately for each month of the agricultural season, with the very beginning of the season on the left side of the graph and the harvest season on the right side of the graph. Interestingly, the coefficient for the fourth month of the season is actually positive. It is hard to know exactly why this is the case, but it could be an interaction between the positive effects of coal pollution on agricultural productivity found by Sanders and Barreca (2022) and the fact that very little labor is used just prior to harvest. However, the overall explanation is beyond the scope of the current paper.

The other four months all see negative effects of pollution on agricultural productivity. However, the effect during the harvest season is the largest, at more than twice the magnitude of any of the other three months. In other words, it seems that pollution has the largest effects during harvest, which is consistent with the hypothesis that pollution affects labor productivity. This is also consistent with the results in Table \ref{tab:yieldrice}, which show that pollution has larger effects in rice-growing areas, which are more labor intensive.

@@

Importantly, since these results come from an IV, both coefficients denote the change in agricultural yield due to an increase in pollution by the same units. In other words, this is not identifying differences in overall pollution, per se, but rather differences in the effects of an increase of pollution by the same amount. These different effects could be due to, for example, differences in emission patterns for different kinds of plants and factories; coal plants, for example, are responsible for much more mercury than other kinds of polluting industries.\footnote{\url{https://www.epa.gov/sites/default/files/2016-12/documents/nei2014v1_tsd.pdf}}

\hypertarget{quantifying-the-overall-effects-of-pollution-on-agricultural-productivity}{%
\section{Quantifying the overall effects of pollution on agricultural productivity}\label{quantifying-the-overall-effects-of-pollution-on-agricultural-productivity}}

Pollution has increased markedly in India over the last few decades. We can use the results above to quantify the overall effects of pollution on agricultural productivity. However, there are two reasons just using the sample of villages from the main results above might not be indicative of overall changes in India. First, the sample of villages have higher levels of pollution than other villages, as shown in Table \ref{tab:plantresultstable}. Second, the sample of villages are also located near coal plants, which appear to have larger negative effects on agricultural productivity than other sources of pollution.

For this reason, I instead turn to data from ICRISAT,\footnote{\url{http://data.icrisat.org/dld}} which has district-level total production data from different years. To track with the timing of the main data used above, I pull total agricultural production from 2001 and 2011 for three of the most common crops in India: rice, wheat, and maize. To simplify the calculation, I assume total area devoted to each crop is unchanged across the decade. I then merge this with the pollution data from Hammer et al. (2020) using a 2011 district-level census shapefile, which has identifiers that match the ICRISAT data. Figure \ref{fig:yielddatamaps} in the appendix shows the distribution of total output for the three crops in 2001. The data covers much, but not all, of the country.

In the output data, I observe values for 2001 and 2011. I can calculate the overall change in log output across the two years, as well as the overall change in pollution levels. I use the most conservative point estimate \emph{without} coal plants in \ref{tab:yield7ivdiffindiff}, which is \(-0.223\). For each district, I calculate the counterfactual for each crop as follows:
\begin{gather} \label{eq:counterfactual} \Delta log(\mathrm{counterfactual})_{d}-0.223\times\Delta log(PM2.5)_{d} = \Delta log(\mathrm{actual})_{d}, \end{gather}

where \(\mathrm{counterfactual}\) is the value I want to calculate, while \(\mathrm{actual}\) is the actual observed change in output. I invert the equation to find the predicted counterfactual without the change in pollution. In other words, I calculate what the change would have been if pollution had not changed at all for any given district. Since this relies on log changes, I restrict the sample only to districts that have output data for a given crop in 2001. Due to a few very large changes in pollution in a few areas, I winsorize log counterfactual changes at the 95th percentile for all crops. After calculating the counterfactual for each district separately, I sum total output to the country level in order to judge the overall effects of pollution on agricultural productivity.

The overall change depends on the distribution of changes in pollution as well as the distribution of output across the three crops. I first present the actual and predicted changes in (log) output in Figures \ref{fig:yield9counterfactual1}, \ref{fig:yield9counterfactual2}, and \ref{fig:yield9counterfactual3} in the appendix. Since pollution increased almost everywhere, the counterfactual change is (almost) always higher than the actual change.

I present the main results of the back-of-the-envelope calculation in Table \ref{tab:counterfactualsums}. I align the three crops across the rows, with the 2001 and 2011 total output (summed across all districts, in '000s of tons) in the first two columns. Total actual output increased for all three crops, with the largest absolute increase being for wheat -- which increased by around 37 percent in relative terms -- and the largest relative increase being for maize -- which increased by around 60 percent in total output.

The key set of results is the comparison betweens column two and column three. Column two gives the actual total output by crop in 2011, while column three presents the counterfactual output, calculated as what would have happened if pollution had not changed at all. There is quite a bit of heterogeneity across crops. For rice, total output would have been around 2.3 percent higher if pollution had remained at 2001 levels. Maize, on the other hand, would have seen a 4.2 percent increase and wheat would have seen a 3.8 percent increase. These results underscore the point that the effects of pollution are not uniform across crops, even if we assume equal effects of pollution, due to differences in the distribution of pollution changes across the country.

\caption{\label{tab:counterfactualsums}Change in output and counterfactual, all districts}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
 & 2001 actual output & 2011 actual output & 2011 counterfactual & Difference (pct.)\\
\midrule
Rice & 79,962 & 93,238 & 95,405 & 2.3\\
Wheat & 58,780 & 93,975 & 97,520 & 3.8\\
Maize & 11,935 & 20,897 & 21,832 & 4.5\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Output is the total sum across all districts, in '000s of tons. The counterfactual is calculated as described in Equation 5.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Particulate matter (log PM 2.5) & -0.042*** & -0.045*** & -0.008** & -0.041***\\
 & (0.003) & (0.003) & (0.003) & (0.003)\\
Weather & No & Yes & Yes & No\\
Weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes\\
\midrule
Observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

@@

\begin{figure}
\includegraphics{draft_files/figure-latex/yielddatamaps-1} \caption[The maps show the district-level yields of each crop in 2001]{The maps show the district-level yields of each crop in 2001.}\label{fig:yielddatamaps}\floatfoot*{Yield data comes from ICRISAT.}
\end{figure}

\begin{landscape}
\begin{figure}
\includegraphics{draft_files/figure-latex/yield9counterfactual1-1} \caption[Distribution of actual and counterfactual log changes in output, rice]{Distribution of actual and counterfactual log changes in output, rice}\label{fig:yield9counterfactual1}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\includegraphics{draft_files/figure-latex/yield9counterfactual2-1} \caption[Distribution of actual and counterfactual log changes in output, wheat]{Distribution of actual and counterfactual log changes in output, wheat}\label{fig:yield9counterfactual2}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\includegraphics{draft_files/figure-latex/yield9counterfactual3-1} \caption[Distribution of actual and counterfactual log changes in output, maize]{Distribution of actual and counterfactual log changes in output, maize}\label{fig:yield9counterfactual3}
\end{figure}
\end{landscape}
